---
title: "5241 HW1 Haiqi Li hl3115"
author: "Haiqi Li"
date: "27/1/2018"
output: pdf_document
---

#Problem 3
##1

First I copied the chart in Wiki with all their symbols to Excel.Then I copied the symbol column and paste with transpose. Finally I get longstring here.

```{r,warning=F}
options("getSymbols.yahoo.warning"=FALSE) 
options("getSymbols.warning4.0"=FALSE) 
options(warn = F)
library(quantmod,warn.conflicts = F)

longstring="AAPL	AXP	BA	CAT	CSCO	CVX	DIS	DWDP	GE	GS	HD	IBM	INTC	JNJ	JPM	KO	MCD	MMM	MRK	MSFT	NKE	PFE	PG	TRV	UNH	UTX	V	VZ	WMT	XOM
"
DJIname <- strsplit(longstring,split = "\t")
DJIname <- DJIname[[1]]#unlist it
DJIname[30] <- "XOM"#final term has a \n
data <- getSymbols("AAPL", auto.assign = F, from = "2017-01-01", to = "2018-01-01")
#initialize data to get number of columns
data <- data[,4]
#since I only use the close price,I pick it up manually

for(i in 2:30){
  datatemp <- getSymbols(DJIname[i], auto.assign = F,
              from = "2017-01-01", to = "2018-01-01")
  #since we only take use of close price,I think to get it first is better
  datatemp <- datatemp[,4]
  data <- cbind.data.frame(data,datatemp)
}
#A for-loop to get other data and put to them into one dataframe.

colnames(data) <- DJIname
for(i in 1:nrow(data)){
  tempname <- substr(rownames(data)[i],start = 6,stop=nchar(rownames(data)[i]))
  rownames(data)[i] <- tempname
}
#rename colunms and rows
```

#2

```{r}
biplot(princomp(data,cor=F))
```

The biplot here is not very informative since all vectors are very condensed in the picture.

```{r}
screeplot(princomp(data,cor=F))
```

The screeplot here shows that component 1 takes most of variance. I think only one component is really important.

#3

```{r}
biplot(princomp(data,cor=T))
```

After modification of scale,I think this time the biplot is much more informatice. I noticed that McDonald and Coca-Cola are very closed to each and they are all food companies.Also,most finacial companies like JPMorgan,Travelers and Visa are of negative component 2 and are closed to each. Maybe Goldman Sachs veries here.

```{r}
screeplot(princomp(data,cor=T))
```

This time,the screelot shows that Component 2 may count for something,too.


#4
```{r}
data <- as.matrix(data)
data.lag <- diff(data,lag=1,differences = 1)
data <- data[-1,]
data.r <- data.lag/data
screeplot(princomp(data.r,cor=T))
```

The screeplot here shows that only component 1 and 2 could not explain all variance.Many other components do make sense.

```{r}
biplot(princomp(data.r,cor=T))
```

The biplot show that all stocks are of negative component 1. I think this tell us some information about the whole market trend since they are all in one direction.

If the stocks fluctuate randomly and independent to each,I think the direction of each stock vector should distribute more uniform, just like a circle. 





